PANCHANGE_analysis

### 2020-11-16 PANCHANGE_analysis.Rmd
education, employment & employment change sensitivity

# GAD prepan
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

@@

# PHQ prepan
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

@@

# OCIR prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

@@

#PCL prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

@@

# GAD prepan
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

@@

# PHQ prepan
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

@@

# OCIR prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

@@

#PCL prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment prior covid sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

@@

# GAD prepan
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment change sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

@@

# PHQ prepan
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment change sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

@@

# OCIR prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment change sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

@@

#PCL prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment change sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

>>>>

# GAD baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b absolute whole sample}
# Regression coefficients
gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_estimates)
gad_baseline_model1b_estimates

# GAD retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b sum_score retro}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

# GAD prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

@@

# PHQ baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b absolute whole sample}
# Regression coefficients
phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1b_estimates)
phq_baseline_model1b_estimates

# PHQ retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b sum_score retro}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

# PHQ prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

@@

# OCIR baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b absolute whole sample}
# Regression coefficients
ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1b_estimates)
ocir_baseline_model1b_estimates

# OCIR retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b sum_score retro}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

# OCIR prepan 
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

@@

# PCL baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivity model1b absolute whole sample}
# Regression coefficients
pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1b_estimates)
pcl_baseline_model1b_estimates

#PCL prepan 
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

@@

# GAD baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment prior covid sensitivity model1b absolute whole sample}
# Regression coefficients
gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_estimates)
gad_baseline_model1b_estimates

# GAD retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment prior covid sensitivity model1b sum_score retro}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

# GAD prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

@@

# PHQ baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment prior covid sensitivity model1b absolute whole sample}
# Regression coefficients
phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1b_estimates)
phq_baseline_model1b_estimates

# PHQ retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment prior covid sensitivity model1b sum_score retro}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

# PHQ prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

@@

# OCIR baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment prior covid sensitivity model1b absolute whole sample}
# Regression coefficients
ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1b_estimates)
ocir_baseline_model1b_estimates

# OCIR retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment prior covid sensitivity model1b sum_score retro}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

# OCIR prepan 
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

@@

# PCL baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment prior covid sensitivity model1b absolute whole sample}
# Regression coefficients
pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1b_estimates)
pcl_baseline_model1b_estimates

#PCL prepan 
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment prior covid sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

@@

# GAD baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment change sensitivity model1b absolute whole sample}
# Regression coefficients
gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_estimates)
gad_baseline_model1b_estimates

# GAD retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment change sensitivity model1b sum_score retro}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

# GAD prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment change sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

@@

# PHQ baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment change sensitivity model1b absolute whole sample}
# Regression coefficients
phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1b_estimates)
phq_baseline_model1b_estimates

# PHQ retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment change sensitivity model1b sum_score retro}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

# PHQ prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment change sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

@@

# OCIR baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment change sensitivity model1b absolute whole sample}
# Regression coefficients
ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1b_estimates)
ocir_baseline_model1b_estimates

# OCIR retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment change sensitivity model1b sum_score retro}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

# OCIR prepan 
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment change sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

@@

# PCL baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment change sensitivity model1b absolute whole sample}
# Regression coefficients
pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1b_estimates)
pcl_baseline_model1b_estimates

#PCL prepan 
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment change sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates
